---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi=200,
  comment = "#>",
  fig.path = "man/figures/README-africa-",
  out.width = "100%"
)
```



# COVID19analytics

 <!-- . -->

This package curate (downloads, clean, consolidate, smooth) [data from Johns Hokpins](https://github.com/CSSEGISandData/COVID-19/) for analysing international outbreak of COVID-19. 
 
It includes several visualizations of the COVID-19 international outbreak.



Yanchang Zhao, COVID-19 Data Analysis with Tidyverse and Ggplot2 - China. RDataMining.com, 2020.

URL: http://www.rdatamining.com/docs/Coronavirus-data-analysis-china.pdf.

* COVID19DataProcessor generates curated series
* [visualizations](https://www.r-bloggers.com/coronavirus-data-analysis-with-r-tidyverse-and-ggplot2/) by [Yanchang Zhao](https://www.r-bloggers.com/author/yanchang-zhao/) are included in ReportGenerator R6 object 
* More visualizations included int ReportGeneratorEnhanced R6 object
* Visualizations ReportGeneratorDataComparison compares all countries counting epidemy day 0 when confirmed cases > n (i.e. n = 100).

# Consideration
Data is still noisy because there are missing data from some regions in some days. We are working on in it.



# Package

<!-- badges: start -->
| Release | Usage | Development |
|:--------|:------|:------------|
| | [![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-blue.svg)](https://cran.r-project.org/) | [![Travis](https://travis-ci.org/rOpenStats/COVID19analytics.svg?branch=master)](https://travis-ci.org/rOpenStats/COVID19analytics) |
| [![CRAN](http://www.r-pkg.org/badges/version/COVID19analytics)](https://cran.r-project.org/package=COVID19analytics) | | [![codecov](https://codecov.io/gh/rOpenStats/COVID19analytics/branch/master/graph/badge.svg)](https://codecov.io/gh/rOpenStats/COVID19analytics) |
|||[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)|
<!-- badges: end -->

# How to get started (Development version)

Install the R package using the following commands on the R console:

```R
# install.packages("devtools")
devtools::install_github("rOpenStats/COVID19analytics", build_opts = NULL)
```

# How to use it

```{r load}
library(COVID19analytics) 
library(dplyr) 

```

```{r}
data.processor <- COVID19DataProcessor$new(provider = "JohnsHopkingsUniversity", missing.values = "imputation")

#dummy <- data.processor$preprocess() is setupData + transform is the preprocess made by data provider
dummy <- data.processor$setupData()
dummy <- data.processor$transform()
# Curate is the process made by missing values method
dummy <- data.processor$curate()

current.date <- max(data.processor$getData()$date)

rg <- ReportGeneratorEnhanced$new(data.processor)
rc <- ReportGeneratorDataComparison$new(data.processor = data.processor)


top.countries <- data.processor$top.countries
international.countries <- unique(c(data.processor$top.countries,
                                    "China", "Japan", "Singapore", "Korea, South"))
africa.countries <- sort(data.processor$countries$getCountries(division = "continent", name = "Africa"))

```

```{r}
# Top 10 daily cases confirmed increment
(data.processor$getData() %>%
  filter(date == current.date) %>%
  select(country, date, rate.inc.daily, confirmed.inc, confirmed, deaths, deaths.inc) %>%
  arrange(desc(confirmed.inc)) %>%
  filter(confirmed >=10))[1:10,]
```


```{r}
# Top 10 daily deaths increment
(data.processor$getData() %>%
  filter(date == current.date) %>%
  select(country, date, rate.inc.daily, confirmed.inc, confirmed, deaths, deaths.inc) %>%
  arrange(desc(deaths.inc)))[1:10,]
```

```{r, dataviz-4-africa-countries}
rg$ggplotTopCountriesStackedBarDailyInc(included.countries = africa.countries,
                                                  countries.text = "Africa")
rc$ggplotComparisonExponentialGrowth(included.countries = africa.countries, min.cases = 20)

rg$ggplotCountriesLines(included.countries = africa.countries, countries.text = "Africa countries",
                        field = "confirmed.inc", log.scale = TRUE)
rc$ggplotComparisonExponentialGrowth(included.countries = africa.countries, 
                                     field = "deaths", y.label = "deaths", min.cases = 1)

```


```{r, dataviz-5-top-countries}
rg$ggplotTopCountriesStackedBarDailyInc(top.countries)
rc$ggplotComparisonExponentialGrowth(included.countries = international.countries, 
                                               min.cases = 100)
```


```{r, dataviz-6-top-countries-inc-daily}
rg$ggplotCountriesLines(field = "confirmed.inc", log.scale = TRUE)
rg$ggplotCountriesLines(field = "rate.inc.daily", log.scale = TRUE)
```


```{r, dataviz-7-top-countries-inc-legacy}
rg$ggplotTopCountriesPie()
rg$ggplotTopCountriesBarPlots()
rg$ggplotCountriesBarGraphs(selected.country = "Ethiopia")
```



